Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
make previous experiment section less crappy

\section{What we already did/background stuff}
Tor is an anonymity tool which is used by a lot of people. It is important (prove this/cite stuff/say something more meaningful about this) and works well. However, there are complaints that Tor is not usable. Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it. But what about the people who are using Tor? what usability issues would thee be if people were not stopped?

To our knowledge, that has been the only user study of Tor. Since then, Tor has a lot of updates. Additionally, there were a lot of features that were untested. We ran a small pilot study on 5 journalists which involved a cognitive walkthrough.(explain cognitive walkthrough if necessary). We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.

Recruitment here. Demographics here. Setup here. Explain that other Tor users could see this as well. How long each the experiment took on average here. (put any misc details or additional methodology things here). The result was that people did have difficulty with X, Y, Z.

>>>>

\section{What we already did/background stuff}
Tor is the most widely used anonymity browser today. However, there are complaints that Tor is not usable. Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it. But what about the people who are using Tor? what usability issues would thee be if people were not stopped?

To our knowledge, that has been the only user study of Tor. Since then, Tor has a lot of updates. Additionally, there were a lot of features that were untested. We ran a small pilot study on 5 journalists which involved a cognitive walk through.(explain cognitive walkthrough if necessary). We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.

We recruited 5 journalists from Berkeley. Demographics here. We recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers. The participants also took an exit survey which estimated their familiarity with technology and security. How long each the experiment took on average here. (put any misc details or additional methodology things here). The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
